---
output: rmarkdown::html_vignette
title: "Removing NA as a Level"
pkgdown:
  as_is: true
description: >
  If you are new to chcRne or are blanking on function names you can find documentation on the functions including  examples here.

vignette: >
  %\VignetteIndexEntry{Code examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  comment = "#>"
)
```

```{r setup}
# Load in necessary librariesand set seed
set.seed(2025)
library(chcRne)
library(dplyr)
```


```{r echo=FALSE}
# First, lets generate some data where `NA` is included as a level
Var1 <- sample(c("Disagree", "Agree", NA), 10, replace = TRUE, prob = c(0.3, 0.4, 0.3))
Var2 <- sample(c("Disagree",  "Agree", NA), 10, replace = TRUE, prob = c(0.3, 0.3, 0.4))
# Convert Var1 and Var2 to factors with NA as a level
Var1 <- factor(Var1, levels = c("Disagree", "Agree"), ordered = TRUE)
Var2 <- factor(Var1, levels = c("Disagree", "Agree"), ordered = TRUE)
Var1 <- addNA(Var1)
Var2 <- addNA(Var2)
na.as.lvl <- data.frame(Var1, Var2)
```

### Applying `remove.na.levels()` to multiple variables

First, lets look at the levels of some of the different variables within the data frame of interest.
```{r}
sapply(na.as.lvl, levels)
```

As we can see in the above output, both Var1 and Var2 have `NA` as a level. Now we apply the `remove.na.levels` to Var1 and Var2.
```{r}
# List out all variable names with NA as a level
cols.with.na.lvls <- na.as.lvl %>% select(where(is.ordered)) %>% names()

# Apply function
na.not.as.lvl <- na.as.lvl |>  mutate(across(all_of(cols.with.na.lvls), ~remove.na.levels(.x)))
```

Now that we have applied the function to the variables of interest, lets check and make sure NA is no longer a level in Var1 and Var2.
```{r}
sapply(na.not.as.lvl, levels)
```

Success! NA is no longer a level in Var1 and `Var2.



