---
title: "CHC Snippets"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{CHC Snippets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r echo=FALSE}
colorize <- function(x, color) {
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{%s}{%s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color,
      x)
  } else x
}
```

## Intro and Purpose
A code snippet is quick way to access code. For example, if you find yourself loading in the dplyr package on a daily basis, you could create snippet called `dp` that contains the code `library(dplyr)`. Then you can type `dp` and hit "tab" and the `library(dplyr)` will appear. You can check what code snippets you have and edit them by going to "Tools" and selecting "Edit Code Snippets". Along with reducing unnecessary typing, snippets are a great way to quickly access code that is easily forgotten. The dplyr syntax for applying a function across multiple columns can be tricky to remember and tedious to find. So we can make snippet, lets call it `ac` that contains `across(COLS), ~ifelse(is.na(.x), 0, 1)`. So, when we type `ac` in the console or a code chunk and hit "tab", `across(COLS), ~ifelse(is.na(.x), 0, 1)`  will appear.


Snippets are not just for R code! You can have snippets for HTML, Quarto, JavaScript, etc.. Lets start with the R code snippets first.

### R
`r colorize("snippet sc", "red")`
  select(starts_with(""))
	
`r colorize("snippet ac", "red")`
  across(COLS), ~ifelse(is.na(.x), 0, 1)
  
### Quarto


### HTML


### Latex


